Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-17 manuscript.tex
minor 5.3  update

In the previous section, we saw that the estimated RV measured when considering a SN or a Normal density resulted in different amplitudes, especially when using the SN mean RV. 
However, once corrected for stellar activity using the linear combination presented in Eq.~\eqref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity, and also compare them when using the usual stellar activity correction with the proposed stellar activity model of Eq.~\eqref{eq:RV:correction}.
To carryout this test, the minimum detected amplitude of an injected planetary signal is estimated at different orbital periods when considering data affected by stellar activity.

>>>>

In the previous section, we saw that the estimated RV resulted in different amplitudes when considering a SN or a Normal density, especially when using the SN mean RV. 
However, once corrected for stellar activity using the linear combination presented in Eq.~\eqref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity, and also compare them when using the usual stellar activity correction with the proposed stellar activity model of Eq.~\eqref{eq:RV:correction}.
To carryout this test, the minimum detected amplitude of an injected planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
